Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions

### 2019-09-16 Manuscript/Manuscript.Rmd
Update MS

bibliography      : ["CANLab_UNL.bib"]

@@

### load necessary libraries ###
suppressPackageStartupMessages(library(readxl)) 
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(openxlsx))
suppressPackageStartupMessages(library(Rmisc))
suppressPackageStartupMessages(library(broom))
```
# Introduction
Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world. In fact, facial expressions are seen across cultures [@ekman_constants_1971] and some evidence suggests expressions are innate (cite). Often, facial expressions serve as a clear social signal, but this is not always the case. While a smile from a friend likely expresses a positive affective state, other cues are not so clear. For instance, a surprised facial expression could signal either a positive (e.g., winning the lottery) or negative (e.g., a snake in the woods) affective state. In the absence of a larger context, individuals differ in their tendency to interpret surprised facial expressions as either positive or negative. Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to both surprised faces and ambiguous scenes [@neta_neural_2013]. This bias towards positive or negative interpretations is known as one's valence bias. 
Interpreting facial expressions requires both bottom-up (e.g., perceptual input) and top-down (e.g., emotion regulation strategies) processes. A growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes, and that arriving at a positive interpretation requires additional, top-down regulatory processes. For example, participants reliably rate surprise as negative faster than positive [@neta_dont_2016]. In fact, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018]. Perceptual input also contributes to valence bias. In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions. In short,  
Despite the trait-like nature of this bias [@neta_corrugator_2009], valence bias may be shifted, at least temporarily, by a number of experimental manipulations. As mentioned above, simple manipulations like slowing response times will shift bias [@neta_its_2018]. Additional work has shown that increases in salivary cortisol after a stressor relate to more negative interpretations of surprised faces from baseline to post-stressor [@brown_cortisol_2017]. Similarly, participants with positive biases at baseline will interpret surprise as more negative under threat of shock [@neta_impact_2017], suggesting that taxing cognitive resources, in this case attention, reduces the ability of individuals to interpret surprised faces as positive.

@@

>>>>

bibliography      : ["HarpNetaInPrep.bib"]

@@

### load necessary libraries ###
suppressPackageStartupMessages(library(readxl)) 
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(openxlsx))
suppressPackageStartupMessages(library(Rmisc))
suppressPackageStartupMessages(library(broom))
```
# Introduction
Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world. Often, facial expressions serve as a clear social signal, but this is not always the case. While a smile likely expresses a positive affective state, other cues are not so clear. For instance, a surprised expression could signal either a positive (e.g., winning the lottery) or negative (e.g., seeing a snake in the woods) affective state in the expresser. When contextual information is limited, individuals differ in their tendency to interpret surprised facial expressions as positive or negative. Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to surprised faces as they do for ambiguous scenes [@neta_neural_2013] or even words (Harp, Petro, Brown & Neta, in prep). This bias towards positive or negative interpretations is known as one's valence bias and myriad factors contribute to one's bias.

Both bottom-up (e.g., perceptual input) and top-down (e.g., stereotypes) processes are recruited for interpretation of facial expressions, and a growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes. For instance, reaction times are faster for negative interpretations of ambiguous stimuli (just faces??) [@neta_dont_2016]. Additionally, presentation of surprised facial expressions as low spatial frequency images, which is processed more readily than high spatial frequency images, biased interpretations towards negativity [@neta_primacy_2010]. Consequently, under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes and there is evidence to support this as well. For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018]. Neuroimaging evidence supports this initial negativity hypothesis as well, more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation [@petro_individual_2018]. <!-- Perceptual input also contributes to valence bias. In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions. THIS NEEDS TO BE REWORKED --> In short, slowing response time allows individuals to better regulate the potentially negative information in surprised expressions and to see it in a more positive light.

<!-- Despite the trait-like nature of this bias [@neta_corrugator_2009], valence bias may be shifted, at least temporarily, by a number of experimental manipulations. As mentioned above, simple manipulations like slowing response times will shift bias [@neta_its_2018]. Additional work has shown that increases in salivary cortisol after a stressor relate to more negative interpretations of surprised faces from baseline to post-stressor [@brown_cortisol_2017]. Similarly, participants with positive biases at baseline will interpret surprise as more negative under threat of shock [@neta_impact_2017], suggesting that taxing cognitive resources, in this case attention, reduces the ability of individuals to interpret surprised faces as positive. -->

Recent work suggests that working memory, while a functional (single?) system, may be distributed and divisible into domain-specific subsystems (e.g., affective working memory; see @mikels_affective_2019). While it is possible to (mostly) isolate perceptual processses (e.g., interpreting emotional facial expressions) under strict laboratory conditions, attention "in the real world" is typically distributed across competing exogenous (e.g., noticing a plane fly above you) and endogenous stimuli (e.g., interoception) (cite). Further, these competing stimuli may be either task-revelevant or task-irrelevant (cite). The literature reports conflicting results for the role of affect on working memory (see @jackson_enhanced_2009 and @mather_emotional_2006), with some suggesting ehnaced recall for emotional stimuli and others reporting impairment in working memory processes. Similarly, working memory also affects emotional processes--converging work suggests that cognitive demands can mitigate negative emotional effects [@dillen_tuning_2008]. Lavie and colleagues -[@lavie_load_2004] suggest a load theory in which cognitive resources are finite, thus limiting the availability for simultaneous processing under large task demands. But, how might concurrent working memory demands affect a more malleable process, like interpreting emotional ambiguity?

Obviously, psychological processes do not occur in a void--that is, it would be quite rare to engage only in a face interpretation task. Instead, people are

@@

Future work should consider whether the representations of these emotional images in AWM (Reuter-Lorenz), or
